### 2019-03-26 3_task_bench.tex
Apply Alex's comments to section 4.
Update section 3 text.

For simplicity but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Many problems can be described by a task graph of
constant width, in which case the iteration space is rectangular, but
Task Bench is capable of handling non-rectangular iteration spaces,
such as required by sweeps and tree-based dependence
patterns. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, each column $i$ corresponds to all tasks
with index $i$ in the iteration space over all the time steps.

Dependencies between tasks are controlled by a configurable dependence
relation. Dependencies point backwards in time. The
dependence relation enumerates, for each task, the set of tasks in the
previous time step that task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, and so on. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs}.

>>>>

For simplicity but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Many problems can be described by a task graph of
constant width, in which case the iteration space is rectangular, but
Task Bench is capable of handling non-rectangular iteration spaces,
such as required by sweeps and tree-based dependence
patterns. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, each column $i$ corresponds to all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column of the task graph will be
assigned to execute on a different processor core.

Dependencies between tasks are controlled by a configurable dependence
relation. Dependencies point backwards in time. The
dependence relation enumerates, for each task, the set of tasks in the
previous time step that task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, and so on. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.
